Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-01-22 paper.tex
including the SOM figures + several updates

After the SOM analysis, the following variables have been selected: 
\emph{retail pricer, reprints, number of reprints, gifts, units distributed as novelty, print-run, total sales }.

@@

%********************************************************************************
\section*{Acknowledgements}
This work has been supported in part by 
PreTEL (PRM Consultores - Trevenque),
TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), 
PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la
IX Convocatoria de Proyectos de Investigaci{\'o}n), 
and PYR-2014-17 GENIL project (CEI-BIOTIC Granada).

>>>>

\begin{figure}[!ht] 
\begin{center}
  \epsfig{file=SOM_25x16_pre_venta.eps,width=15cm}
\caption{\small{SOM analysis.}}
\label{fig:somanalysis}
\end{center}
\end{figure}

\begin{figure}[!ht] 
\begin{center}
  \epsfig{file=UMATRIX_25x16_pre_venta.eps,width=15cm}
\caption{\small{SOM UMATRIX.}}
\label{fig:somumatrix}
\end{center}
\end{figure}

After the SOM analysis (see Figures \ref{fig:somanalysis} and \ref{fig:somumatrix}), the following variables have been selected: 
\emph{retail pricer, reprints, number of reprints, gifts, units distributed as novelty, print-run, total sales }.

@@

%********************************************************************************
\section*{Acknowledgements}

This work has been supported in part by projects 
PreTEL (PRM Consultores - Trevenque),
TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitiveness), 
SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), 
PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), 
PROY-PP2015-06 (Plan Propio 2015 UGR), 
and project CEI2015-MP-V17 of the Microprojects program 2015 from CEI BioTIC Granada.
